Tor's Usability for Censorship Circumvention

### 2015-10-05 paper/circumvention-experiment.tex
make unfinished things red

\begin{abstract}

Tor has grown beyond its original purpose as and has 
since become an important Internet circumvention tool.
We specifically examine it usability as a censorship circumvention tool,
an essential facet for adoption and use.  
We focus our analysis on the connection configuration dialog of Tor browser,
as censorship circumvention requires correct transport configurations. %%
Our talk will describe a future study aimed at evaluating 
if and how easily users can circumvent censorship using Tor Browser,
isolating specific browser features to study in the process. 
To this end, we will conduct a large-scale user study examining hundreds of users 
on how they navigate Tor's configuration wizard to complete seven browsing tasks 
in three different adversarial settings. 
We solicit feedback to improve our study's design.
\end{abstract}

@@

\section{Tor's Usability}
%Idea is to cover background on Tor's usability as an anonymity tool, and then highlight the shift in focus to evaluating Tor's usability as a censorship circumvention tool.

@@

After our first  usability evaluation of Tor, it was clear to us that so many of the features had been left unevaluated---such as advanced web browsing tasks, the configuration menu, automatic updates, and identity and cookie management. 
%say something about how we resolved this somehow, and how it doesn't necessarily need our attention now
We found that the most effective way to resolve the problems encountered was more user guidance and interface remodeling rather than continued user observations.
%emphasize how we are aiming for new research, not new test cases for debugging an interface
Rather than selecting the features to study in isolation, 
we decided to focus on an important use case of Tor browser, censorship circumvention. 
%say something along the lines of ``x people are using it for this, and there's no work on it,'' 
%if there are stats on this type of thing.
To our knowledge, this is the first user study investigating the usability of Tor as a 
censorship circumvention tool, rather than an anonymity tool.

@@

\noindent {\bfseries Overview}
% test tor, test improvements, may do followups on demand, push changes.

%improve what is below:
For users to circumvent censorship in their resident countries, they will need to configure Tor to set up a proxy, bridge, or both. There is a configuration wizard to help guide users through setting up their connection, but our hypothesis is that the average user will not easily be able to configure Tor correctly in these adverse settings, as they require the user to provide IP addresses of proxies or bridges to use. The goal of our experiment is to see how successful users are at carrying out common browsing tasks in an adversarial setting using Tor.

@@

\noindent {\bfseries Experiment Flow} 
% explain one experiment from start to end. 
At the start of the study, participants will be informed
of the role they they will be playing in the study. Particularly,
they will be informed that they are in a censorship environment
which prevents them from visiting certain websites, but they
are people who would like to visit those websites for 
leisurely purposes.

@@

We start off the experiment by telling them that they are in an adversarial setting, and that some websites are blocked and some websites are not. We will instruct them to visit notblocked.com and also blocked.com to illustrate the situation that they are in. We will also explain what Tor is, and how they can use it if necessary, and ask them to complete the set of tasks. To complete all the tasks, the participants will ultimately need to get the correct configuration settings for the country they are simulated to be in. We will end the experiment with a survey which asks them things like their security background, tech exposure, what was unexpected, what was hard, etc. We plan to analyze: which configuration tasks are hard (bridges versus proxies, etc.), how many were successful, how long it took users to configure, if they understood the process, if they were confident that it was working as expected, etc. \\

\noindent {\bfseries Censorship Environment Simulation} 
We plan to simulate three censorship environments.
They are informed by our experience with pluggable transports
and knowledge of commonly seen censorship techniques.
They are not meant perfectly to replicate the network environment
in any particular country; rather, they are abstract simulations
that are nevertheless inspired by reality.

@@

In certain real censorship environment and our most 
prohibitive simulated censorship environments, only some of 
Tor's pluggable transports work in censorship environments
where others do not. Some of them require additional information
(like bridge addresses) before they work. Currently, we do not 
have a way to target test specific transports. However, we 
do ask why participants chose a specific pluggable 
transport in our exit survey to gain some insight.\\

>>>>

\begin{abstract}
{\color{red}
Tor has grown beyond its original purpose as and has 
since become an important Internet circumvention tool.
We specifically examine it usability as a censorship circumvention tool,
an essential facet for adoption and use.  
We focus our analysis on the connection configuration dialog of Tor browser,
as censorship circumvention requires correct transport configurations.
Our talk will describe a future study aimed at evaluating 
if and how easily users can circumvent censorship using Tor Browser,
isolating specific browser features to study in the process. 
To this end, we will conduct a large-scale user study examining hundreds of users 
on how they navigate Tor's configuration wizard to complete seven browsing tasks 
in three different adversarial settings. 
We solicit feedback to improve our study's design.}
\end{abstract}

@@

\section{Tor's Usability}
{\color {red}
%Idea is to cover background on Tor's usability as an anonymity tool, and then highlight the shift in focus to evaluating Tor's usability as a censorship circumvention tool.

@@

After our first  usability evaluation of Tor, it was clear to us that so many of the features had been left unevaluated---such as advanced web browsing tasks, the configuration menu, automatic updates, and identity and cookie management. 
%say something about how we resolved this somehow, and how it doesn't necessarily need our attention now
We found that the most effective way to resolve the problems encountered was more user guidance and interface remodeling rather than continued user observations.
%emphasize how we are aiming for new research, not new test cases for debugging an interface
Rather than selecting the features to study in isolation, 
we decided to focus on an important use case of Tor browser, censorship circumvention. 
%say something along the lines of ``x people are using it for this, and there's no work on it,'' 
%if there are stats on this type of thing.
To our knowledge, this is the first user study investigating the usability of Tor as a 
censorship circumvention tool, rather than an anonymity tool. }

@@

\noindent {\bfseries Overview}
{\color {red}
% test tor, test improvements, may do followups on demand, push changes.

%improve what is below:
For users to circumvent censorship in their resident countries, they will need to configure Tor to set up a proxy, bridge, or both. There is a configuration wizard to help guide users through setting up their connection, but our hypothesis is that the average user will not easily be able to configure Tor correctly in these adverse settings, as they require the user to provide IP addresses of proxies or bridges to use. The goal of our experiment is to see how successful users are at carrying out common browsing tasks in an adversarial setting using Tor.}\\

@@

\noindent {\bfseries Experiment Flow} 
{\color {red}
% explain one experiment from start to end. 
At the start of the study, participants will be informed
of the role they they will be playing in the study. Particularly,
they will be informed that they are in a censorship environment
which prevents them from visiting certain websites, but they
are people who would like to visit those websites for 
leisurely purposes.

@@

We start off the experiment by telling them that they are in an adversarial setting, and that some websites are blocked and some websites are not. We will instruct them to visit notblocked.com and also blocked.com to illustrate the situation that they are in. We will also explain what Tor is, and how they can use it if necessary, and ask them to complete the set of tasks. To complete all the tasks, the participants will ultimately need to get the correct configuration settings for the country they are simulated to be in. We will end the experiment with a survey which asks them things like their security background, tech exposure, what was unexpected, what was hard, etc. We plan to analyze: which configuration tasks are hard (bridges versus proxies, etc.), how many were successful, how long it took users to configure, if they understood the process, if they were confident that it was working as expected, etc.} \\

\noindent {\bfseries Censorship Environment Simulation} 
{\color{red}
We plan to simulate three censorship environments.
They are informed by our experience with pluggable transports
and knowledge of commonly seen censorship techniques.
They are not meant perfectly to replicate the network environment
in any particular country; rather, they are abstract simulations
that are nevertheless inspired by reality.

@@

In certain real censorship environment and our most 
prohibitive simulated censorship environments, only some of 
Tor's pluggable transports work in censorship environments
where others do not. Some of them require additional information
(like bridge addresses) before they work. Currently, we do not 
have a way to target test specific transports. However, we 
do ask why participants chose a specific pluggable 
transport in our exit survey to gain some insight.}\\
